Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-16 article/article.tex
(+) notations

>>>>

In this section, we discuss the model established to approach this configuration
problem. First we defined a structure for a controled sector and all possible
transitions through time. Then a workload model is defined. And finally we
determined a cost per partition and a cost function aimed to be minimized.

\subsection{State}

\subsection{workload}

$p_{low}$
$p_{normal}$
$p_{high}$

\subsection{Partition cost and cost function}

In order to evaluate a given partition $P$ at time $t$, a cost $C(P, t)$ needs
to be defined. This cost depend on the workload in each the sector. We give the
following intermediate definitions to represent a high (respectively normal
and low) cost for the partition :
\begin{itemize}
    \item $c_+(P, t) = \sum_{S \in P_t} \delta_{h}(S, t) * p_{high}^{S, t} * |S|^2$
    \item $c_=(P, t) = \sum_{S \in P_t} \delta_{n}(S, t) * p_{norm}^{S} * |S|^{-2}$
    \item $c_-(P, t) = \sum_{S \in P_t} \delta_{l}(S, t) * p_{low}^{S, t} * |S|^{-2}$
\end{itemize}
with $\delta_{h}(P, t)$ (resp. $\delta_{n}(P_t)$ and $\delta_{l}(P_t)$) equal 1
if the probability $p_{high}$ (resp. $p_{normal}$ and $p_{low}$) is superior to
the two other, and 0 otherwise.

With

\section*{Notation}

\begin{itemize}
    \item $m$ : elementary module
    \item $S$ : sector control position, group of modules
    \item $P$ : partition of the airspace, group of sectors
    \item $t$ : current time
    \item $C(P, t)$ : Cost of a given partition $P$ at time $t$
    \item $s$ : state, in this article a partition $P$ and a time $t$
    \item $h(s)$ : heuristic that gives for a state $s$ an estimation of the cost
    \item $\mu_{F, a}$ : mean of all reward comming from node $F$ with action $a$
    \item $T_F$ : number of simuation where the final path include the node $F$
    \item $T_{F, a}$ : number of simuation where the final path include the node $F$ with action $a$
\end{itemize}
